The Astropy Project

### 2017-11-11 main.tex
approx not sim

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
The commit distribution follows an approximate power-law (with log-slope of
$\sim -0.47$), meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
$\approx 50$ percent of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.

>>>>

As of version 2.0, \astropypkg contains $212244$ lines of code\footnote{This
line count includes comments, as these are often as important for
maintainability as the code itself.  Without comments there are $142197$ lines
of code.} contributed by $232$ unique contributors over $19270$ \texttt{git}
commits.
The commit distribution follows an approximate power-law (with log-slope of
$\approx -0.47$), meaning most of the commits were and are contributed by a
relatively small fraction of the contributor pool.
$\approx 50$ percent of the commits were contributed by the top $4$
contributors, while $\sim 90$ percent of the commits came from the top $24$
contributors.
